---
title: "Initial Checks"
format: html
---

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(knitr)
library(ggrepel)
```

I'm loading a csv file that includes the following variables:

- country: The name of the country\*
- pings: The average daily number of pings in the dataset during May 2024
- devices: The average number of devices in the dataset during May 2024
- pop_k: The estimated population in the country (in thousands) on January 1, 2023\*

\* from https://population.un.org/wpp/downloads?folder=Standard%20Projections&group=Most%20used

I'm going to calculate:
* The number of pings per device on an average day and
* The number of devices per thousand people

```{r}
summary <- here("data.csv") |>
    read_csv(show_col_types = FALSE) |>
    mutate(pings_per_device = pings/devices,
           devices_per_pop_k = devices/pop_k)

head(summary) |>
    kable()
```

I'm also going to separate out a few countries of interest.


```{r}
subset_names <- c("Canada",
                  "United States of America",
                  "Brazil",
                  "Germany",
                  "Sweden",
                  "Indonesia",
                  "Republic of Korea",
                  "Chile",
                  "Norway",
                  "France",
                  "Argentina",
                  "Singapore",
                  "Poland",
                  "Greece",
                  "Holy See")

subset <- summary |>
    filter(country %in% subset_names)
```

Now I'll compare the number of devices per person to the number of pings per device.


```{r}
options(ggrepel.max.overlaps = Inf)

ggplot(summary) +
    geom_point(aes(x = devices_per_pop_k,
                   y = pings_per_device),
               size = 1,
               alpha = 0.5) +
    geom_point(data = subset,
               aes(x = devices_per_pop_k,
                   y = pings_per_device),
               color = "darkorange",
               size = 2) +
    geom_text_repel(data = subset,
                    aes(x = devices_per_pop_k,
                        y = pings_per_device,
                        label = country),
                    color = "darkorange") +
    scale_x_continuous(transform = "log10",
                       name = "Number of devices per thousand people",
                       breaks = breaks <- 10^seq(-2, 3, by=1),
                       labels = formatC(breaks, format = "f", digits = 2)) +
    scale_y_continuous(transform = "log10") +
    theme_minimal()
```